### 2016-03-11 paper/stereo.tex
yasu

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it slow
due to the overhead.  Therefore, we pick parallel
alpha-expansion~\cite{delong} and hierarchical fusion~\cite{delong,olga}
with graph-cuts optimization as the competing methods.

\mysubsubsection{Swarm fusion architectures}

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SFWSS (SF without solution sharing), SFWMF (SF without
multi-way fusion), and the standard SF.
%
For SFWSS, we have chosen $\alpha=2$ ($\beta=0$). For SFWMF, each thread
iterates the step of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so
that it can take a solution proposal in one step and a neighboring
solution in the next. For the standard SF, we have used ($\alpha=1, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our proposal
generation to be constant-label proposals. Graph-cuts is used in fusing
a constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it slow
due to the overhead.  Therefore, we have chosen Parallel
Alpha Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
with graph-cuts optimization as the competing methods.

\mysubsubsection{Swarm Fusion architectures}

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
For SF-SS, we have chosen $\alpha=2$ ($\beta=0$). For SF-MF, each thread
iterates the step of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so
that it can take a solution proposal in one step and a neighboring
solution in the next. For the standard SF, we have used ($\alpha=1, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our proposal
generation to be constant-label proposals. Graph-cuts is used in fusing
a constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
